\vspace{-2.0em} Move Schedules: Fast persistence computations in coarse dynamic settings \thanks{ \textbf{Funding:} This work was partially supported by the National Science Foundation through grants CCF-2006661 and CAREER award DMS-1943758. }

### 2023-01-31 move_schedules.tex
amending prop 2 slightly to be more transparent
typo fixes

If our goal is to decrease the size of $\lvert S_F \rvert$, one option is to \emph{coarsen} $S_F$ to a new schedule $\widetilde{S}_F$ by collapsing contiguous sequences of adjacent transpositions to moves, via the map:
\begin{equation}\label{eq:tr_to_mv}
	 (i, i+1)(i+1, i+2)\cdots(j-1, j) \mapsto (j, i+1, \cdots, j-1, i)  \quad \text{ if } i < j
\end{equation}
We expect $\widetilde{S}_F$ to be cheaper to execute than $S_F$, with the tradeoff  that less diagrams are produced.
We make this precise next:
\begin{proposition}\label{prop:factor2}
	Let $K$ denote a filtration of size $\lvert K \rvert = m$ with decomposition $R = D V$, $T$ the maximum number of $O(m)$ operations required to execute $S_F$ via vineyards, and $M$ be the maximum number of $O(m)$ operations required to execute $\widetilde{S}_F$ with moves. Then, the inequality $ M \leq {\textstyle \frac{1}{2} \, T}$ holds.
\end{proposition}
\begin{proof} \normalsize
First, consider executing the vineyards algorithm on a given schedule $S_F$. As there are at most $2$ column operations, any contiguous sequence of transpositions $(i,i+1), (i+1,i+2), \ldots (j-1,j)$ induces at most $2(\lvert i - j \rvert)$ column operations in both $R$ and $V$, giving a total of $4(\lvert i - j \rvert)$ column operations.

>>>>

If our goal is to decrease the size of $\lvert S_F \rvert$, one option is to \emph{coarsen} $S_F$ to a new schedule $\widetilde{S}_F$ by collapsing contiguous sequences of adjacent transpositions to moves, via the map:
\begin{equation}\label{eq:tr_to_mv}
	 (i, i+1)(i+1, i+2)\cdots(j-1, j) \mapsto (j, i+1, \cdots, j-1, i)  \quad \text{ if } i < j
\end{equation}
We expect $\widetilde{S}_F$ to be cheaper to execute using move operations than $S_F$, with the tradeoff  that less diagrams are produced.
We make this precise next:
\begin{proposition}\label{prop:factor2}
	Let $K$ denote a filtration of size $\lvert K \rvert = m$ with decomposition $R = D V$, $T$ the maximum number of $O(m)$ operations required to execute $S_F$ via vineyards, and $M$ be the maximum number of $O(m)$ operations required to execute $\widetilde{S}_F$ with moves. Then, if all pairs $(i, j) \in \tilde{S}_F$ satisfy $i < j$ and $\lvert i - j \rvert > 1$, the inequality $ M \leq {\textstyle \frac{1}{2} \, T}$ holds.
\end{proposition}
\begin{proof} \normalsize
First, consider executing the vineyards algorithm on a given schedule $S_F$. As there are at most $2$ column operations, any contiguous sequence of transpositions $(i,i+1), (i+1,i+2), \ldots (j-1,j)$ induces at most $2(\lvert i - j \rvert)$ column operations in both $R$ and $V$, giving a total of $4(\lvert i - j \rvert)$ column operations.
